00_datawrangling.Rmd

### 2020-08-06 analysis/00_datawrangling.Rmd
revisiting kallisto

```{r countData}
# import count data, set rows at entreziz
kallistodata <- read.table("../results/kallistocounts.txt", 
                        sep = ",", row.names = NULL) %>%
  rename("NCBI" = "entrezid",
         "gene" = "Name")
#head(kallistodata)

>>>>

```{r countData}
# import count data, set rows at entreziz
kallistodata <- read.table("../results/kallistocounts.txt", 
                        sep = ",", row.names = NULL) 
kallistodata <- kallistodata %>%
  dplyr::rename("NCBI" = "entrezid",
         "gene" = "Name")
head(kallistodata)
